### 2022-04-13 about/vita_professional.tex
Shovelling trouble and new title for indepno

\leftright{Citizen of Canada and Singapore}{3660 Rue Hutchison, Apt.\ 4}
\leftright{Email: marcel\_goh@yahoo.ca}{Montr\'eal, QC H2X 2H3, Canada}
\leftright{Webpage: marcelgoh.ca}{+1\thinspace\up(825\up)\thinspace 440-0681}

@@

\begingroup\frenchspacing
\papercount=4
\pubbegin P
\papitem (with Luc Devroye and Rosie Y. Zhao)
The independence number of a Bienaym\'e--Galton--Watson tree
and related parameters. To appear in {\sl Combinatorics, Probability and Computing}, 20~pp. [arXiv:2106.14389]
\papitem (with Anna M. Brandenberger, Luc Devroye, and Rosie Y. Zhao)
Leaf multiplicity in a Bienaym\'e--Galton--Watson tree. {\sl Discrete Mathematics
and Theoretical Computer Science} {\bf 24},1 (2022), \#7, 16~pp. [arXiv:2105.12046]
\papitem (with Anna M. Brandenberger and Luc Devroye)
Root estimation in Galton--Watson trees. To appear in {\sl Random Structures and Algorithms}, 24~pp.
[arXiv:2007.05681]
\papitem (with Rosie Y. Zhao)
Arithmetic subsequences in a random ordering of an additive set.
{\sl Integers: Electronic Journal of Combinatorial Number Theory} {\bf 21} (2021), \#A89, 19~pp.
[arXiv:2012.12339]

@@

@@

\leftright{\bf Probabilistic analysis of branching processes}{\bf May 2020 -- present}
\leftright{\sl Research group}{\sl McGill University}
\smallskip
Ongoing research on branching processes, headed by Luc Devroye. Studied estimation problems
on Galton-Watson trees. Attended informal seminars, discussing
various topics related to branching
processes and other topics in probability and combinatorics.
(Gave a presentation at six of these: one on root estimation in Galton-Watson
trees, two on generating functions and elementary analytic combinatorics, two on graph regularity, and
one concerning two of Erd\H os's proofs on prime numbers.)

\medbreak
\leftright{\bf Sorting algorithms on manifolds}{\bf May -- August 2020}
\leftright{\sl Summer research project}{\sl McGill University}
\smallskip
Research project under the supervision of Michael Lipnowski.
Studied algorithms that investigate the topology of group actions on locally symmetric spaces.
Work involved writing of code in OCaml and PostScript that generates illustrations of certain quotient
spaces, in various models of hyperbolic geometry.
\medbreak

@@

\leftright{\bf Bytecode compiler and interpreter}{\bf February -- June 2019}
\leftright{\sl Individual software project}{\sl Charles University}
\smallskip
Semester-long individual software project under the supervision of Adam Dingle.
Created OPythn, a bytecode compiler and virtual machine for a subset of Python.
OPythn includes support for lists, dictionaries, named and anonymous functions, objects, and classes.
It is implemented in OCaml using Ocamllex for lexing and Menhir for parsing.

>>>>

\leftright{+1\thinspace\up(825\up)\thinspace 440-0681}{3660 Rue Hutchison, Apt.\ 4}
\leftright{Email: marcel\_goh@yahoo.ca}{Montr\'eal, QC H2X 2H3, Canada}
\leftright{Webpage: marcelgoh.ca}{}

@@

\begingroup\frenchspacing
\papercount=4
\pubbegin P
\papitem (with Luc Devroye and Rosie Y. Zhao)
On the peel number and the leaf-height of a Galton--Watson tree.
To appear in {\sl Combinatorics, Probability and Computing}, 20~pp. [arXiv:2106.14389]
\papitem (with Anna M. Brandenberger, Luc Devroye, and Rosie Y. Zhao)
Leaf multiplicity in a Bienaym\'e--Galton--Watson tree. {\sl Discrete Mathematics
and Theoretical Computer Science} {\bf 24},1 (2022), \#7, 16~pp. [arXiv:2105.12046]
\papitem (with Anna M. Brandenberger and Luc Devroye)
Root estimation in Galton--Watson trees. To appear in {\sl Random Structures and Algorithms}, 24~pp.
[arXiv:2007.05681]
\papitem (with Rosie Y. Zhao)
Arithmetic subsequences in a random ordering of an additive set.
{\sl Integers: Electronic Journal of Combinatorial Number Theory} {\bf 21} (2021), \#A89, 19~pp.
[arXiv:2012.12339]

@@

\sectheader{Selected Software Projects}

\leftright{\bf Tlingit verb parsing}{\bf February -- April 2021}
\smallskip
A rule-based program that finds regularity in Tlingit verbs, written in Python.

\noindent[{\tt https://github.com/marcelgoh/tlingit-verb-parsing}]
\medbreak

\leftright{\bf Sorting algorithms on manifolds}{\bf May -- August 2020}
\smallskip
Research project under the supervision of Michael Lipnowski.
Studied algorithms that investigate the topology of group actions on locally symmetric spaces.
Work involved writing of code in OCaml and PostScript that generates illustrations of certain quotient
spaces, in various models of hyperbolic geometry.

\noindent[{\tt https://github.com/marcelgoh/manifold-sorting}]
\medbreak

\leftright{\bf Bytecode compiler and interpreter}{\bf February -- June 2019}
\smallskip
Under the supervision of Adam Dingle, wrote a bytecode compiler and virtual machine for a subset of Python.
OPythn includes support for lists, dictionaries, named and anonymous functions, objects, and classes.
It is implemented in OCaml using Ocamllex for lexing and Menhir for parsing.

\noindent[{\tt https://github.com/marcelgoh/opythn}]
\medbreak

\leftright{\bf Alonzo $\lambda$-calculus interpreter}{\bf May -- June 2019}
\smallskip
Wrote an interpreter for the untyped $\lambda$-calculus that performs $\alpha$-conversion
and $\beta$-reduction. Includes an interactive environment that allows users to bind names to
terms. Implemented in Haskell.

\noindent[{\tt https://github.com/marcelgoh/alonzo}]
\medbreak

\leftright{\bf Escape-time fractals}{\bf May 2019}
\smallskip
Made an interactive graphical program to generate and explore fractals. Implemented using the SDL2
graphics library and written in \CEE. (HackPrague 2019)

\noindent[{\tt https://github.com/mattonicorp/mattoni}]
\medbreak

\leftright{\bf Nim}{\bf January 2019}
\smallskip
Implemented the game of Nim graphically using Processing. Worked on game logic and created the soundtrack
using an $8$-bit sequencer. (ConUHacks IV)

\noindent[{\tt https://github.com/conudihedral4/nim}]
\medbreak

\leftright{\bf CourseTalk}{\bf November 2018}
\smallskip
Created a web chat app using Node.js and React.js. (HackPrinceton Fall 2018)

\noindent[{\tt https://github.com/marcelgoh/hackprinceton-2018}]
\medbreak

@@

\leftright{\bf Probabilistic analysis of branching processes}{\bf May 2020 -- present}
\leftright{\sl Research group}{\sl McGill University}
\smallskip
Ongoing research on branching processes, headed by Luc Devroye. Studied estimation problems
on Galton-Watson trees. Attended informal seminars, discussing
various topics related to branching
processes and other topics in probability and combinatorics.
(Gave a presentation at six of these: one on root estimation in Galton-Watson
trees, two on generating functions and elementary analytic combinatorics, two on graph regularity, and
one concerning two of Erd\H os's proofs on prime numbers.)
\medbreak

@@
